Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-15 apples_and_oranges.qmd
Playing around with 'key' column, trying to find a solution

# Here I am creating a new column for df_long_for_metan, to be able to identify which studies featured a condition of interest. 
# for CBT, fluox, esc
cbt_fluox_esc_study_ids <- df_with_distinct_instruments %>%
  filter(active_type %in% c("cbt", "Fluoxetine", "Escitalopram")) %>%
  pull(new_study_id)
df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key1 = ifelse(new_study_id %in% cbt_fluox_esc_study_ids, 1, NA))

@@

df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key = paste(key1, key2, sep = "_"))

>>>>

# Here I am creating a new column for df_long_for_metan, to be able to identify which studies featured a condition of interest. 
# for CBT, fluox, esc. I am calling this cfe
cbt_fluox_esc_study_ids <- df_with_distinct_instruments %>%
  filter(active_type %in% c("cbt", "Fluoxetine", "Escitalopram")) %>%
  pull(new_study_id)
df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key1 = ifelse(new_study_id %in% cbt_fluox_esc_study_ids, 1, NA))

@@

# for wl and cau
wl_or_cau_study_ids <- df_with_distinct_instruments %>%
  filter(control_type %in% c("wl", "cau")) %>%
  pull(new_study_id)
df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key3 = ifelse(new_study_id %in% wl_or_cau_study_ids, 3, NA))

# for cdrs only
cdrs_study_ids <- df_with_distinct_instruments %>%
  filter(instrument_name == "cdrs")) %>%
  pull(new_study_id)
df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key4 = ifelse(new_study_id %in% cdrs_study_ids, 4, NA))

df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key = paste(key1, key2, key3, key4, sep = "_"))
